\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-23 paper.tex
added software dev strategy classification diagram

@@

The remainder of this paper proceeds as follows: section \ref{classification}
takes a look at ID algorithms and classifies them. Section \ref{pattern} looks
for patterns in the implementation of these classes of algorithms, details some
of the ideas behind FCF and identifies the different aspects of the problem
space. Section \ref{design} describes the design we applied to construct the
framework, its domain specific language (DSL) and code generator. Section
\ref{evaluation} evaluates an implementation and application of the framework.
Section \ref{related} explores related work in the field of DSLs for ID and
code generation for the IoT. Finally, section \ref{conclusion} summarizes our
findings, draws conclusions and identifies topics for future work.

>>>>

\usepackage{tikz-3dplot}

@@

The remainder of this paper proceeds as follows: section \ref{approach}
classifies our approach as a development strategy for wireless devices, section
\ref{classification} takes a look at ID algorithms and classifies them. Section
\ref{pattern} looks for patterns in the implementation of these classes of
algorithms, details some of the ideas behind FCF and identifies the different
aspects of the problem space. Section \ref{design} describes the design we
applied to construct the framework, its domain specific language (DSL) and code
generator. Section \ref{evaluation} evaluates an implementation and application
of the framework. Section \ref{related} explores related work in the field of
DSLs for ID and code generation for the IoT. Finally, section \ref{conclusion}
summarizes our findings, draws conclusions and identifies topics for future
work.

\section{Classification of Code Generation as a Development Strategy}
\label{approach}

Figure \ref{fig:approach} shows a classification of several development
strategies that can be adopted for projects involving wireless devices.

\begin{figure}[ht]
\tdplotsetmaincoords{110}{-10}
\begin{tikzpicture}[scale=1,tdplot_main_coords]
  % axis
  \draw[very thick,->] (0,0,0) -- (7,0,0) node[anchor=north east,xshift=8mm]{$flexibility$};
  \draw[very thick,->] (0,0,0) -- (0,7,0) node[anchor=north west]{$update$};
  \draw[very thick,->] (0,0,0) -- (0,0,4) node[anchor=south]{$development$};
  % points
  \coordinate (O)        at (0,0,0);
  \coordinate (ideal)    at (6,0,0);
  \coordinate (vm)       at (2,2,2);
  \coordinate (modular)  at (4,4,4);
  \coordinate (reconfig) at (4,2,4);
  \coordinate (full)     at (6,6,4);
  \coordinate (cg)       at (6,4.5,3);
  % "lines"
  \draw[dashed] (2,0,0)    -- (2,2,0) -- (0,2,0);
  \draw[dashed] (4,0,0)    -- (4,4,0) -- (0,4,0);
  \draw[dashed] (6,0,0)    -- (6,6,0) -- (0,6,0);
  \draw[dashed] (vm)       -- (2,2,0);
  \draw[dashed] (modular)  -- (4,4,0);
  \draw[dashed] (full)     -- (6,6,0);
  \draw[dashed] (reconfig) -- (4,2,0);
  \draw[dashed] (cg)       -- (6,4.5,0);
  % "balls"
  % 1. ideal
  \tdplottransformmainscreen{6}{0}{0}
  \shadedraw[tdplot_screen_coords, ball color=lightgray,draw=lightgray]
    (\tdplotresx,\tdplotresy) circle (0.20)
    node[above,xshift=+5pt,yshift=+5pt,text=gray]{\footnotesize ideal};
  % 2. VM
  \tdplottransformmainscreen{2}{2}{2}
  \shadedraw[tdplot_screen_coords, ball color=lightgray,draw=lightgray]
    (\tdplotresx,\tdplotresy) circle (0.20)
    node[above,yshift=+7pt,text=gray]{\footnotesize virtual machine};
  % 3. modular
  \tdplottransformmainscreen{4}{4}{4}
  \shadedraw[tdplot_screen_coords, ball color=lightgray,draw=lightgray]
    (\tdplotresx,\tdplotresy) circle (0.20)
    node[left,xshift=-5pt,text=gray]{\footnotesize modular native image};
  % 4. reconfig
  \tdplottransformmainscreen{4}{2}{4}
  \shadedraw[tdplot_screen_coords, ball color=lightgray,draw=lightgray]
    (\tdplotresx,\tdplotresy) circle (0.20)
    node[above,yshift=+7pt,text=gray]{\footnotesize reconfigurable virtual machine};
  % 5. full
  \tdplottransformmainscreen{6}{6}{4}
  \shadedraw[tdplot_screen_coords, ball color=lightgray,draw=lightgray]
    (\tdplotresx,\tdplotresy) circle (0.20)
    node[right,xshift=+5pt,text=gray]{\footnotesize full native image};
  % 5. cg
  \tdplottransformmainscreen{6}{4.5}{3}
  \shadedraw[tdplot_screen_coords, ball color=gray,draw=black]
    (\tdplotresx,\tdplotresy) circle (0.20)
    node[right,xshift=+5pt,text=black,align=center]{\footnotesize code generation};
\end{tikzpicture}
\caption{Classification of Development Strategies for Wireless Devices (based on \cite{sadilek2007energy})}
\label{fig:approach}
\end{figure}
